The host galaxy of the short GRB~111117A at $z = 2.211$\thanks{Based on observations collected at the European Southern Observatory, Paranal, Chile, Program ID: 088.A-0051 and 091.D-0904.}

### 2017-06-27 GRB111117A.tex
Fixing affil, adding ack

\keywords{Gamma-ray burst: individual: GRB~111117A --- }

@@

Although a single burst carries little leverage in terms of constraining the
redshift distribution of sGRB, the high redshift of GRB~111117A needs to be
accommodated in progenitor models. A lognormal delay time model predicts a very
low volumetric density of bursts at $z = 2.211$, whereas a power law delay time
model peaks near GRB~111117A. If more sGRBs are at similarly high redshifts, but
are missed due to the faintness of their hosts, a lognormal delay time model
will be disfavored. Compared to a sample of sGRB hosts, GRB~111117A is more
luminous than 80 per cent of a complete sample of sGRB hosts with measured
luminosities. For between 43 and 71 per cent of sGRB hosts, we would be unable
to determine a redshift should they be at a similar redshift as GRB~111117A.
This could indicate that potentially, a significant fraction of sGRBs are at
high $z$ but missed due to host faintness.

@@

TK acknowledges support through the Sofja Kovalevskaja Award to P. Schady. 
CT acknowledges support from a Spanish National Research Grant of Excellence under project AYA 2014-58381-P and funding associated to a Ramón y Cajál fellowship under grant number RyC-2012-09984.
AdUP acknowledges support from a Ramón y Cajal fellowship, a BBVA Foundation Grant for Researchers and Cultural Creators,and the Spanish Ministry of Economy and Competitiveness through project AYA2014-58381-P.
Partly based on observations made with the Gran Telescopio Canarias (GTC).
ZC acknowledges support from the Spanish research project AYA 2014-58381-P and support from Juan de la Cierva Incorporaci\'on fellowships IJCI-2014-21669. 
RSR acknowledges AdUP's BBVA Foundation Grant for Researchers and Cultural Creators

>>>>

\keywords{Gamma-ray burst: individual: GRB~111117A -- Gamma-ray burst: general -- Galaxies: high-redshift -- binaries: general -- X-rays: bursts -- Techniques: imaging spectroscopy}

@@

Although a single burst carries little leverage in terms of constraining the
redshift distribution of sGRB, the high redshift of GRB~111117A needs to be
accommodated in progenitor models. A lognormal delay time model predicts a very
low volumetric density of bursts at $z = 2.211$, whereas a power law delay time
model peaks near GRB~111117A. If more sGRBs are at similarly high redshifts, but
are missed due to the faintness of their hosts, a lognormal delay time model
will be disfavored. Compared to a sample of sGRB hosts, GRB~111117A is more
luminous than 80 per cent of a complete sample of sGRB hosts with measured
luminosities. Assuming a host brightness redshift determination threshold, for
between 43 and 71 per cent of sGRB hosts, we would be unable to determine a
redshift should they be at a similar redshift as GRB~111117A. This could
indicate that potentially, a significant fraction of sGRBs are at high $z$ but
missed due to host faintness.

@@

TK acknowledges support through the Sofja Kovalevskaja Award to P. Schady.
% 
JJ acknowledges support from NOVA and NWO-FAPESP grant for advanced
instrumentation in astronomy.
%
CT acknowledges support from a Spanish National Research Grant of Excellence
under project AYA 2014-58381-P and funding associated to a Ramón y Cajál
fellowship under grant number RyC-2012-09984.
%
AdUP acknowledges support from a Ramón y Cajal fellowship, a BBVA Foundation
Grant for Researchers and Cultural Creators,and the Spanish Ministry of Economy
and Competitiveness through project AYA2014-58381-P. Partly based on
observations made with the Gran Telescopio Canarias (GTC).
%
ZC acknowledges support from the Spanish research project AYA 2014-58381-P and
support from Juan de la Cierva Incorporaci\'on fellowships IJCI-2014-21669.
%
RSR acknowledges AdUP's BBVA Foundation Grant for Researchers and Cultural
Creators and support from ASI (Italian Space Agency) through the Contract n. 2015-046-R.0 and from European Union Horizon 2020 Programme under the AHEAD project (grant agreement n. 654215).
%
This research made use of Astropy, a community-developed core Python package for Astronomy \citep{TheAstropyCollaboration2013}. The analysis and plotting has been achieved using the Python-based packages Matplotlib \citep{Hunter2007}, Numpy and Scipy \citep{VanderWalt2011} along with other community-developed packages.

### 2017-06-27 authorlist.tex
Addressing Susannas comments
Closes #11
Small edit to include limit on missed fraction
Fix affil
Fixing affil, adding ack

\author{J.~Selsing\inst{1}
\and T.~Kr\"{u}hler\inst{2}
\and D.~Malesani\inst{1,3}
\and P.~D'Avanzo\inst{4}
\and J.~Palmerio\inst{5}
\and S.~D.~Vergani\inst{6}
\and J.~Japelj\inst{7}
\and B.~Milvang-Jensen\inst{1}
\and D.~Watson\inst{1}
\and P.~Jakobsson\inst{8}
%
\and Z.~Cano\inst{9}
%\and L.~B.~Christensen\inst{1}
\and V.~D'Elia\inst{10}
\and A.~de~Ugarte~Postigo\inst{9, 1}
\and J.~P.~U.~Fynbo\inst{1}
\and A.~Gomboc\inst{11}
\and K.~E.~Heintz\inst{8,1}
\and A.~J.~Levan \inst{12}
\and S.~Schulze \inst{13, 14}
\and M.~Sparre\inst{1,15}
\and N.~R.~Tanvir\inst{16}
\and C.~C.~Th\"one\inst{9}
}

\institute{Dark Cosmology Centre, Niels Bohr Institute, University of Copenhagen, Juliane Maries Vej 30, 2100 K\o benhavn \O, Denmark
%2
\and Max-Planck-Institut f\"{u}r extraterrestrische Physik, Giessenbachstra\ss e, 85748 Garching, Germany
%3
\and DTU Space, National Space Institute, Technical University of Denmark, Elektrovej 327, DK-2800 Lyngby, Denmark
%4
\and INAF - Osservatorio Astronomico di Brera, via E. Bianchi 46, I-23807, Merate (LC), Italy
%5
\and Sorbonne Universités, UPMC Univ. Paris 6 et CNRS, UMR 7095, Institut d’Astrophysique de Paris, 98 bis bd Arago, 75014 Paris, France
%6
\and GEPI, Observatoire de Paris, PSL Research University, CNRS, Univ. Paris Diderot, Sorbonne Paris Cité, 5 Place Jules Janssen, 92195 Meudon, France
%7
\and Anton Pannekoek Institute for Astronomy, University of Amsterdam, Science Park 904, 1098 XH Amsterdam, The Netherlands
%8
\and Centre for Astrophysics and Cosmology, Science Institute, University of Iceland, Dunhagi 5, 107 Reykjav\'ik, Iceland
%9
\and Instituto de Astrof\'isica de Andaluc\'ia (IAA-CSIC), Glorieta de la Astronom\'ia s/n, E-18008, Granada, Spain.
%10
\and INAF-Osservatorio Astronomico di Roma, Via Frascati 33, I-00040 Monteporzio Catone, Italy;
ASI-Science Data Centre, Via del Politecnico snc, I-00133 Rome, Italy
%11
\and Centre for Astrophysics and Cosmology, University of Nova Gorica, Vipavska 13, 5000 Nova Gorica, Slovenia.
%12
\and Department of Physics, University of Warwick, Coventry CV4 7AL, UK
%13
\and Instituto de Astrof\'isica, Facultad de F\'isica, Pontificia Universidad Cat\'olica de Chile, Vicu\~{n}a Mackenna 4860, 7820436 Macul, Santiago, Chile
%14
\and Millennium Institute of Astrophysics, Vicu\~{n}a Mackenna 4860, 7820436 Macul, Santiago, Chile
%15
\and Heidelberger Institut f{\"u}r Theoretische Studien, Schloss-Wolfsbrunnenweg 35, 69118 Heidelberg, Germany 
%16
\and Department of Physics and Astronomy, University of Leicester, University Road, Leicester, LE1 7RH, UK
%\and European Southern Observatory, Alonso de C\'{o}rdova 3107, Vitacura, Casilla 19001, Santiago 19, Chile
}

>>>>

\author{J.~Selsing\inst{1}
\and T.~Kr\"{u}hler\inst{2}
\and D.~Malesani\inst{1,3}
\and P.~D'Avanzo\inst{4}
\and S.~Schulze \inst{5, 6, 7}
\and J.~Palmerio\inst{8}
\and S.~D.~Vergani\inst{9}
\and J.~Japelj\inst{10}
\and B.~Milvang-Jensen\inst{1}
\and D.~Watson\inst{1}
\and P.~Jakobsson\inst{11}
%
\and J.~Bolmer \inst{2}
\and Z.~Cano\inst{12}
\and S.~Covino \inst{13}
%\and L.~B.~Christensen\inst{1}
\and V.~D'Elia\inst{13, 14}
\and A.~de~Ugarte~Postigo\inst{12, 1}
\and J.~P.~U.~Fynbo\inst{1}
\and A.~Gomboc\inst{15}
\and K.~E.~Heintz\inst{11,1}
\and A.~J.~Levan \inst{16}
\and S.~Piranomonte \inst{17}
\and G.~Pugliese \inst{10}
\and R.~S\'{a}nchez-Ram\'{\i}rez \inst{12, 18}
\and M.~Sparre\inst{1,19}
\and N.~R.~Tanvir\inst{20}
\and C.~C.~Th\"one\inst{12}
\and K.~Wiersema \inst{20}
}

\institute{Dark Cosmology Centre, Niels Bohr Institute, University of Copenhagen, Juliane Maries Vej 30, 2100 K\o benhavn \O, Denmark
%2
\and Max-Planck-Institut f\"{u}r extraterrestrische Physik, Giessenbachstra\ss e, 85748 Garching, Germany
%3
\and DTU Space, National Space Institute, Technical University of Denmark, Elektrovej 327, DK-2800 Lyngby, Denmark
%4
\and INAF - Osservatorio Astronomico di Brera, via E. Bianchi 46, I-23807, Merate (LC), Italy
%5
\and Instituto de Astrof\'isica, Facultad de F\'isica, Pontificia Universidad Cat\'olica de Chile, Vicu\~{n}a Mackenna 4860, 7820436 Macul, Santiago, Chile
%6
\and Millennium Institute of Astrophysics, Vicu\~{n}a Mackenna 4860, 7820436 Macul, Santiago, Chile
%7
\and Department of Particle Physics and Astrophysics, Faculty of Physics, Weizmann Institute of Science, Rehovot 76100, Israel
%8
\and Sorbonne Universités, UPMC Univ. Paris 6 et CNRS, UMR 7095, Institut d’Astrophysique de Paris, 98 bis bd Arago, 75014 Paris, France
%9
\and GEPI, Observatoire de Paris, PSL Research University, CNRS, Univ. Paris Diderot, Sorbonne Paris Cité, 5 Place Jules Janssen, 92195 Meudon, France
%10
\and Anton Pannekoek Institute for Astronomy, University of Amsterdam, Science Park 904, 1098 XH Amsterdam, The Netherlands
%11
\and Centre for Astrophysics and Cosmology, Science Institute, University of Iceland, Dunhagi 5, 107 Reykjav\'ik, Iceland
%12
\and Instituto de Astrof\'isica de Andaluc\'ia (IAA-CSIC), Glorieta de la Astronom\'ia s/n, E-18008, Granada, Spain
%13
\and INAF-Osservatorio Astronomico di Roma, Via Frascati 33, I-00040 Monteporzio Catone, Italy
%14
\and ASI-Science Data Centre, Via del Politecnico snc, I-00133 Rome, Italy
%15
\and Centre for Astrophysics and Cosmology, University of Nova Gorica, Vipavska 13, 5000 Nova Gorica, Slovenia.
%16
\and Department of Physics, University of Warwick, Coventry CV4 7AL, UK
%17
\and INAF, Osservatorio Astronomico di Brera, Via E. Bianchi 46, I-23807 Merate (LC), Italy
%18
\and Istituto de Astrofisica e Planetologia Spaziali, INAF, Via Fosso del Cavaliere 100, I-00133 Roma, Italy
%19
\and Heidelberger Institut f{\"u}r Theoretische Studien, Schloss-Wolfsbrunnenweg 35, 69118 Heidelberg, Germany 
%20
\and Department of Physics and Astronomy, University of Leicester, University Road, Leicester, LE1 7RH, UK
%\and European Southern Observatory, Alonso de C\'{o}rdova 3107, Vitacura, Casilla 19001, Santiago 19, Chile
}
